---
title: "Sentiment Analysis for Blogs - R Notebook"
output: html_notebook
---

#Analysis of "joe-rogans-secret-to-success-strategic-quitting " blog from www.goalcast.com 


Loading the required packages

```{r}
library("SnowballC")
library("tm")
library("syuzhet")
library("rvest")
library("sentimentr")
library("SnowballC")
library("twitteR")
library(sentiment)

```


Before you extract the URL from the any website, do follow the below steps,

1) Open https://www.google.com/chrome/

2) Click on extensions or directly open https://chrome.google.com/webstore/category/extensions?h1=en

3) Type Selector Gadget in search or directly open
https://chrome.google.com/webstore/detail/selectorgadget/mhjhnkcfbdhnjickkkdbjoemdmbfginb?h1=en

4) Bookmark it and Add this extension to chrome, enable it if it shows any prompt

5) Now open any website from where you wanted to extract the text data from.

6) Once you open the website and open any article in it, you should be able to see the extension "Selector Gadget" in chrome       
(magnifying glass icon) and click on various lines in the article until you see yellow color on the web page, once you see yellow color below click on Xpath and copy and the paste the link below in the code near Xpath.



```{r}
url <- 'https://www.goalcast.com/2019/10/09/joe-rogans-secret-to-success-strategic-quitting/'
Blog <- read_html(url)
Blog <- html_nodes(Blog, xpath = "//p")
Blogtext <- html_text(Blog)
Blogtext
typeof(Blogtext)

```

```{r}

some_txt <- Blogtext


#REMOVE PEOPLE
some_txt=gsub("@\\W","",some_txt)

#REMOVE PUNCT

some_txt=gsub("[[:punct:]]","",some_txt)

#remove numbers
some_txt=gsub("[[:digit:]]","",some_txt)

#remove links
some_txt=gsub("http\\w+","",some_txt)

#remove unnecesary spaces

some_txt=gsub("[ \t]{2,}","",some_txt)
some_txt=gsub("^\\s+|\\s+$","",some_txt)


#define lowererror hancling function()

try.error=function(x)
{ #CREATE MISSING VALUE
  y=NA
  #TRY CTACH ERROR
  try.error=tryCatch()
  
}

try.error=function(x)
{ #CREATE MISSING VALUE
  y=NA
  #TRY CTACH ERROR
  try.error=tryCatch(tolower(x), error=function(e) e)
  #if not an error
  if(!inherits(try.error,"error"))
    y=tolower(x)
  #result
  return(y)
  
}


head(some_txt)

some_txt=sapply(some_txt, try.error)

#REMOVE NA's in some_txt
some_txt=some_txt[!is.na(some_txt)]
names(some_txt) = NULL
```



Perform sentiment analysis

```{r}
library(sentiment)
library(Rstem)
library(tm)
library(devtools)
library(sentiment)

#CLASSIFY EMOTION
class_emo=classify_emotion(some_txt, algorithm = "bayes", prior=1.0)

#get emotion best fit
emotion=class_emo[,7]

#substitute NA's by unknown
# classify emotion
class_emo = classify_emotion(some_txt, algorithm="bayes", prior=1.0)
# get emotion best fit
emotion = class_emo[,7]
# substitute NA's by "unknown"
emotion[is.na(emotion)] = "unknown"

# classify polarity
class_pol = classify_polarity(some_txt, algorithm="bayes")
# get polarity best fit
polarity = class_pol[,4]


#Create data frame with the results and obtain some general statistics

# data frame with results
sent_df = data.frame(text=some_txt, emotion=emotion,
                     polarity=polarity, stringsAsFactors=FALSE)

# sort data frame
sent_df = within(sent_df,
                 emotion <- factor(emotion, levels=names(sort(table(emotion), decreasing=TRUE))))

#Let's do some plots of the obtained results
# plot distribution of emotions
# plot distribution of emotions

ggplot(sent_df, aes(x=emotion)) +
  geom_bar(aes(y=..count.., fill=emotion)) +
  scale_fill_brewer(palette="Dark2") +
  labs(x="emotion categories", y="number of tweets")

```


From the above graph, it is clear that joe-rogans-secret-to-success-strategic-quitting blog has more unknown emotions as highest and the next followed by Joy emotion.


```{r}
# plot distribution of polarity

ggplot(sent_df, aes(x=polarity)) +
  geom_bar(aes(y=..count.., fill=polarity)) +
  scale_fill_brewer(palette="RdGy") +
  labs(x="polarity categories", y="number of tweets")

```


Conclusion: From the above graph, it is clear that joe-rogans-secret-to-success-strategic-quitting blog has more positive polarity.


```{r}
#Separate the text by emotions and visualize the words with a comparison cloud
# separating text by emotion
emos = levels(factor(sent_df$emotion))
nemo = length(emos)
emo.docs = rep("", nemo)
for (i in 1:nemo)
{
  tmp = some_txt[emotion == emos[i]]
  emo.docs[i] = paste(tmp, collapse=" ")
}

# remove stopwords
emo.docs = removeWords(emo.docs, stopwords("english"))
# create corpus
corpus = Corpus(VectorSource(emo.docs))
#error
tdm = TermDocumentMatrix(corpus)

#Error in tolower(txt)
tdm = as.matrix(tdm)
colnames(tdm) = emos

# comparison word cloud
comparison.cloud(tdm, colors = brewer.pal(nemo, "Dark2"),
                 scale = c(3,.5), random.order = FALSE, title.size = 1.5)
```


#Lets Analyse which are positive and negative tweets and which are highest in number

```{r}
#converting character into dataframe
test.vector <- as.data.frame((Blogtext))
df<-test.vector
class(df)

names(df)[1]<-"text"
colnames(df)


```


```{r}
#cleaning the dataframe

tweets.df2 <- gsub("http.*","", df$text)

word.df <- as.vector(tweets.df2)
emotion.df <- get_nrc_sentiment(word.df)
emotion.df2 <- cbind(tweets.df2, emotion.df) 


```


```{r}
#finding the sentiment

sent.value <- get_sentiment(word.df)
most.positive <- word.df[sent.value == max(sent.value)]
most.positive


```


```{r}
most.negative <- word.df[sent.value <= min(sent.value)] 
most.negative 


```


```{r}
sent.value

```


```{r}
#Identifying the most positive lines
positive.tweets <- word.df[sent.value > 0]
head(positive.tweets)

```

```{r}
#Identifying the most negative lines
negative.tweets <- word.df[sent.value < 0]
head(negative.tweets)

```


```{r}
#Identifying the neutral lines
neutral.tweets <- word.df[sent.value == 0]
head(neutral.tweets)

```


```{r}
category_senti <- ifelse(sent.value < 0, "Negative", ifelse(sent.value > 0, "Positive", "Neutral"))

senti_graph<-table(category_senti)
senti_graph

```

```{r}

#plotting the graph positive,negative,neutral
barplot(senti_graph,main="Success_Blog",col=c("darkblue","yellow","red"))

```

From the above graph, it is clear that joe-rogans-secret-to-success-strategic-quitting blog has more positive Tweets.


THANK YOU






